Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex
All filter transmission curves from SVO.

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{System throughput (fractional photon detection efficiency) of the
filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel
mode for the various surveys in GZH. The unfilled black curves show the filters
for the Suprime Camera on the \textit{Subaru} telescope, which was used to
create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

>>>>

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on \subaru, which
was used to create color gradients in the GZH COSMOS
images.\label{fig:filtercurves}}
\end{figure*}
